Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\sqrt{s_{\rm NN}}$ = 2.76 TeV

### 2018-01-15 longSC.tex
main part wo funding and ref

\section{Introduction}
\label{sec:intro}
The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting QCD matter, the Quark-Gluon Plasma (QGP). 
The matter produced in a heavy-ion collision exhibits strong collective radial expansion~\cite{PhysRevD.34.794,Heinz:2013th}. 
Difference in pressure gradients and the interactions among matter constituents produced in the spatially anisotropic overlap region of the two colliding nuclei result in anisotropic transverse flow in the momentum space.
The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr,Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} is also observed at LHC energies~\cite{Aamodt:2010pa,ALICE:2011ab,Abelev:2014pua,Adam:2016izf,ATLAS:2011ah,ATLAS:2012at,Aad:2013xma,Aad:2014eoa,Chatrchyan:2012wg,Chatrchyan:2012ta,Chatrchyan:2012xq}. The measurements are well described by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of the QGP in heavy-ion collisions at RHIC and LHC energies is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de}.

The temperature dependence of $\eta/s$ has some generic features typical to the most known fluids. This ratio reaches its minimum value close to the phase transition region~\cite{Kovtun:2004de,Lacey:2006bc}.
It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature. Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be conjectured using AdS/CFT correspondence~\cite{Kovtun:2004de}. Hydrodynamical simulations constrained by data support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental study~\cite{Lacey:2006bc,Csernai:2006zz}.

Anisotropic flow~\cite{Ollitrault:1992bk} is quantified with $n^{\mathrm{th}}$-order flow harmonics $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:

\begin{equation}
E\frac{\mathrm{d}^3N}{\mathrm{d^3}{p}} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
\label{Eq:Fourier}
\end{equation}

\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic. Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the angular brackets denote an average over all particles in all events.
The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
This profile fluctuates event-by-event due to fluctuating positions of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlations between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.

@@

An important input to the hydrodynamic model simulations is the initial distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricities $\epsilon_n$~\cite{Alver:2010gr},
\begin{equation}
 \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
  \label{eq:eccentricities}
\end{equation}
where the curly brackets denote the average over the transverse plane, i.e. $\{\cdots\}$ = $\int$ d$x$d$y$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $\phi$ is azimuthal angle, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonics, $v_2$ and $v_3$, to a good approximation, are linearly proportional to the deformations in the initial energy density in the transverse plane (e.g. $v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
Higher order ($n > 3$) flow harmonics can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
For instance, $v_4$ can develop both as a linear response to $\varepsilon_4$ and/or as a nonlinear response to $\varepsilon_2^2$~\cite{Gardim:2011xv}.
Therefore, the higher harmonics ($n > 3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva,Acharya:2017zfg}. When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitudes of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ are sensitive to the ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
Hence, studies of the correlations between higher order ($n>3$) and lower order ($v_2$ or $v_3$) harmonics and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.

The first results for new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the \textit{Symmetric Cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
The new observables are particularly robust against few-particle nonflow correlations~\cite{Aamodt:2010pa} and they provide independent, complementary information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
In this article, we have extended the analysis of SC observables to higher order harmonics (up to $5^{\mathrm{th}}$ order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also present a systematic comparison to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we present the analysis methods and summarize our findings from the previous work~\cite{ALICE:2016kpq}. The experimental setup and measurements are described in Sec.~\ref{sec:experiment}. The sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. The results of the measurements are presented in Sec.~\ref{sec:results}. In Sec.~\ref{sec:theory} we present comparisons to model calculations.
Finally, Sec.~\ref{sec:summary} summarizes our new results.

@@

Existing measurements for anisotropic flow observables provide an estimate of the average value of $\eta/s$ of the QGP, both at RHIC and LHC energies. What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$). The temperature dependence of $\eta/s$ of the QGP was discussed in~\cite{Csernai:2006zz}. The effects on hadron spectra and elliptic flow were studied in~\cite{Niemi:2011ix} for different parameterizations of $\eta/s(T)$.  A more systematic study with event-by-event EKRT+viscous hydrodynamic calculations was recently initiated in~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein). The emerging picture is that the study of individual flow harmonics $v_n$ alone is unlikely to reveal the details of the temperature dependence of $\eta/s$.
It was already demonstrated in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between amplitudes of two different harmonics $v_m$ and $v_n$. These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their measurement would provide experimental constraints on theoretical parameters used to describe the individual stages of the heavy-ion system evolution. In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.

For reasons discussed in \cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the set of observables introduced in \cite{Niemi:2012aj}. 
Based on \cite{Bilandzic:2013kga}, new flow observables obtained from multiparticle correlations, \textit{Symmetric Cumulants}~(SC), were introduced.

The SC observables are defined as:
 %
%\begin{widetext}
\begin{eqnarray}
\mathrm{SC}(m,n) \equiv \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
&&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
&=&\left<v_{m}^2v_{n}^2\right>-\left<v_{m}^2\right>\left<v_{n}^2\right>\,,%\nonumber\\
%&=&0\,.
\label{eq:4p_cumulant}
\end{eqnarray}
%\end{widetext}
%
with the condition $m\neq n$ for two positive integers $m$ and $n$ (for details see Sec.~IV~C in~\cite{Bilandzic:2013kga}).
In this article SC($m$,$n$) normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq} is denoted by NSC($m$,$n$):
%
\begin{equation}
\mathrm{NSC}(m,n) \equiv \frac{\mathrm{SC}(m,n)}{\left<v_{m}^2\right>\left<v_{n}^2\right>}\,.
\label{eq:nsc}
\end{equation}
%
Normalized symmetric cumulants reflect only the strength of the correlation between $v_{m}$ and $v_{n}$, while SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics. In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$ which suppresses biases from few-particle nonflow correlations. For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}) the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this observable. This was verified by HIJING model simulations in \cite{ALICE:2016kpq}.

The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated for all centralities~\cite{ALICE:2016kpq}. It was found that the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}. The observed centrality dependence of SC(4,2) cannot be captured by models with constant $\eta/s$, indicating that the temperature dependence of $\eta/s$ plays an important role. These results were also used to discriminate between different parameterizations of initial conditions. It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}. 
The first theoretical studies of SC observables can be found in \cite{Zhou:2015eya,Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.

\section{Data Analysis}
\label{sec:experiment}
The data sample of $\PbPb$ collisions at the centre-of-mass energy $\snn=2.76$~TeV analyzed in this article was recorded by ALICE during the 2010 heavy-ion run of the LHC.
Detailed descriptions of the ALICE detector can be found
in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
Projection Chamber (TPC) was used to reconstruct charged particle
tracks and measure their momenta with full azimuthal coverage in the
pseudorapidity range $|\eta|<0.8$. Two scintillator
arrays (V0A and V0C) which cover the pseudorapidity  ranges $-3.7<\eta<-1.7$
and $2.8<\eta<5.1$ were used for triggering and the determination of
centrality~\cite{Aamodt:2010cz}. The trigger
conditions and the event selection criteria are identical to those
described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
Approximately $10^7$ minimum-bias $\PbPb$ events with
a reconstructed primary vertex within $\pm 10$ cm from the nominal
interaction point along the beam direction are selected. Only charged particles reconstructed in the TPC in $|\eta|<0.8$
and $0.2<p_{\rm T}<5$~GeV/$c$ were included in the analysis. The charged track quality cuts
described in~\cite{Aamodt:2010pa} were applied to minimize
contamination from secondary charged particles and fake tracks.
The track reconstruction efficiency and contamination
were estimated from HIJING Monte Carlo
simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
the collision centrality. The reconstruction efficiency increases with transverse momenta from
70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
constant at $(80 \pm 5)$\% for $p_{\rm T}>1$~GeV/$c$. The estimated
contamination by secondary charged particles from weak decays and
photon conversions is less than 6\% at $p_{\rm T}=0.2$~GeV/$c$ and falls
below 1\% for $p_{\rm T}>1$~GeV/$c$.
The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effects of jets on the measured correlations. 
Reconstructed TPC tracks constrained to vertex are required to have at least 70 space points (out of a maximum of 159). 
Only tracks with a transverse distance of closest approach to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted. This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc. Tracks with kinks (i.e. tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.

@@

The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution for the whole centrality range analyzed. The systematic uncertainty from the centrality determination was evaluated by using the TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors. 
The systematic uncertainty on the symmetric cumulants which arises from the centrality uncertainty is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of the nominal interaction to ensure uniform detector acceptance for tracks within $|\eta|<0.8$. The systematic uncertainty from the $z$-vertex cut was estimated by reducing the $z$-vertex range to 8~cm and was found to be less than 3\%.

>>>>

\section{Introduction}
\label{sec:intro}
The main emphasis of the ultrarelativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting QCD matter, the quark-gluon plasma (QGP). 
The matter produced in a heavy-ion collision exhibits strong collective radial expansion~\cite{PhysRevD.34.794,Heinz:2013th}. 
Difference in pressure gradients and the interactions among matter constituents produced in the spatially anisotropic overlap region of the two colliding nuclei result in anisotropic transverse flow in the momentum space.
The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr,Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} is also observed at LHC energies~\cite{Aamodt:2010pa,ALICE:2011ab,Abelev:2014pua,Adam:2016izf,ATLAS:2011ah,ATLAS:2012at,Aad:2013xma,Aad:2014eoa,Chatrchyan:2012wg,Chatrchyan:2012ta,Chatrchyan:2012xq}. The measurements are well described by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of the QGP in heavy-ion collisions at RHIC and LHC energies is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de}.

The temperature dependence of $\eta/s$ has some generic features typical to the most known fluids. This ratio reaches its minimum value close to the phase transition region~\cite{Kovtun:2004de,Lacey:2006bc}.
It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature. Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be conjectured using anti-de sitter/conformal field theory (AdS/CFT) correspondence~\cite{Kovtun:2004de}. Hydrodynamical simulations constrained by data support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental study~\cite{Lacey:2006bc,Csernai:2006zz}.

Anisotropic flow~\cite{Ollitrault:1992bk} is quantified with $n{\mathrm{th}}$-order flow harmonics $v_n$ and corresponding symmetry plane angles $\Psi_n$ in a Fourier decomposition of the particle azimuthal distribution in the plane transverse to the beam direction~\cite{Voloshin:1994mz,Poskanzer:1998yz}:

\begin{equation}
E\frac{{d}^3N}{{d^3}{p}} = \frac{1}{2\pi}\frac{{d}^2N}{p_{\mathrm{T}}{d}p_{\mathrm{T}}{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
\label{Eq:Fourier}
\end{equation}

\noindent where $E$, $p$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n{\mathrm{th}}$-order harmonic. Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the angular brackets denote an average over all particles in all events.
The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
This profile fluctuates event-by-event due to fluctuating positions of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlations between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.

@@

An important input to the hydrodynamic model simulations is the initial distribution of energy density in the transverse plane (the initial density profile), which is usually estimated from the probability distribution of nucleons in the incoming nuclei.
This initial energy density profile can be quantified by calculating the distribution of the spatial eccentricities $\epsilon_n$~\cite{Alver:2010gr},
\begin{equation}
 \varepsilon_{n} e^{in\Phi_{n}} = -\{r^n e^{in\phi}\}/ \{r^n\},
  \label{eq:eccentricities}
\end{equation}
where the curly brackets denote the average over the transverse plane, i.e. $\{\cdots\}$ = $\int$ $d$$x$$d$$y$\, $e(x,y,\tau_0)$ $(\cdots)$, $r$ is the distance to the system's center of mass, $\phi$ is azimuthal angle, $e(x,y,\tau_0)$ is the energy density at the initial time $\tau_0$, and $\Phi_{n}$ is the participant plane angle (see Refs.~\cite{Teaney:2010vd,Niemi:2015qia}).
There is experimental and theoretical evidence~\cite{Alver:2010gr,Qiu:2011iv,ALICE:2011ab} that the lower order harmonics, $v_2$ and $v_3$, to a good approximation, are linearly proportional to the deformations in the initial energy density in the transverse plane (e.g., $v_n \propto \varepsilon_n$ for $n~=~$2 or 3).
Higher order ($n > 3$) flow harmonics can arise from initial anisotropies in the same harmonic~\cite{Alver:2010gr,Teaney:2010vd,Gubser:2010ui,Hatta:2014jva} (linear response) or can be induced by lower order harmonics~\cite{Bravina:2013xla,Bravina:2013ora} (nonlinear response).
For instance, $v_4$ can develop both as a linear response to $\varepsilon_4$ and/or as a nonlinear response to $\varepsilon_2^2$~\cite{Gardim:2011xv}.
Therefore, the higher harmonics ($n > 3$) can be understood as superpositions of linear and nonlinear responses, through which they are correlated with lower order harmonics~\cite{Teaney:2012ke,Bravina:2013ora,Gubser:2010ui,Hatta:2014jva,Acharya:2017zfg}. When the order of the harmonic is large, the nonlinear response contribution in viscous hydrodynamics is dominant and increases in more peripheral collisions~\cite{Teaney:2012ke,Bravina:2013ora}.
The magnitudes of the viscous corrections as a function of $p_{\rm T}$ for $v_4$ and $v_5$ are sensitive to the ansatz used for the viscous distribution function, a correction for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad,Teaney:2012ke}.
Hence, studies of the correlations between higher order ($n>3$) and lower order ($v_2$ or $v_3$) harmonics and their $p_{\rm T}$ dependence can help to understand the viscous correction to the momentum distribution at hadronic freeze-out which is among the least understood parts of hydrodynamic calculations~\cite{Dusling:2009df,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.

The first results for new multiparticle observables which quantify the relationship between event-by-event fluctuations of two different flow harmonics, the \textit{symmetric cumulants}~(SC), were recently reported by the ALICE Collaboration~\cite{ALICE:2016kpq}.
The new observables are particularly robust against few-particle nonflow correlations~\cite{Aamodt:2010pa} and they provide independent, complementary information to recently analyzed symmetry plane correlators~\cite{Aad:2014fla}. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of correlations between different order harmonics would constrain both the initial conditions and the medium properties~\cite{ALICE:2016kpq,Zhu:2016puf}.
In this article, we have extended the analysis of SC observables to higher order harmonics (up to fifth order) as well as to the measurement of the $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also present a systematic comparison to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we present the analysis methods and summarize our findings from the previous work~\cite{ALICE:2016kpq}. The experimental setup and measurements are described in Sec.~\ref{sec:experiment}. The sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. The results of the measurements are presented in Sec.~\ref{sec:results}. In Sec.~\ref{sec:theory} we present comparisons to model calculations.
Finally, Sec.~\ref{sec:summary} summarizes our new results.

@@

Existing measurements for anisotropic flow observables provide an estimate of the average value of $\eta/s$ of the QGP, both at RHIC and LHC energies. What remains uncertain is how the $\eta/s$ of the QGP depends on temperature ($T$). The temperature dependence of $\eta/s$ of the QGP was discussed in Ref.~\cite{Csernai:2006zz}. The effects on hadron spectra and elliptic flow were studied in Ref.~\cite{Niemi:2011ix} for different parametrizations of $\eta/s(T)$.  A more systematic study with event-by-event Eskola-Kajantie-Ruuskanen-Tuominen (EKRT) + viscous hydrodynamic calculations was recently initiated in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities were investigated (see Fig.~1 therein). The emerging picture is that the study of individual flow harmonics $v_n$ alone is unlikely to reveal the details of the temperature dependence of $\eta/s$.
It was already demonstrated in Ref.~\cite{Niemi:2015qia} that different $\eta/s(T)$ parametrizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between amplitudes of two different harmonics $v_m$ and $v_n$. These new observables have the potential to discriminate between the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their measurement would provide experimental constraints on theoretical parameters used to describe the individual stages of the heavy-ion system evolution. In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.

For reasons discussed in Refs.~\cite{ALICE:2016kpq,Bilandzic:2013kga}, the correlations between different flow harmonics cannot be studied experimentally with the set of observables introduced in Ref.~\cite{Niemi:2012aj}. 
Based on Ref.~\cite{Bilandzic:2013kga}, new flow observables obtained from multiparticle correlations, \textit{symmetric cumulants}~(SC), were introduced.

The SC observables are defined as:
 %
%\begin{widetext}
\begin{eqnarray}
\mathrm{SC}(m,n) \equiv \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>_c &=& \left<\left<\cos(m\varphi_1\!+\!n\varphi_2\!-\!m\varphi_3-\!n\varphi_4)\right>\right>\nonumber\\
&&{}-\left<\left<\cos[m(\varphi_1\!-\!\varphi_2)]\right>\right>\left<\left<\cos[n(\varphi_1\!-\!\varphi_2)]\right>\right>\nonumber\\
&=&\left<v_{m}^2v_{n}^2\right>-\left<v_{m}^2\right>\left<v_{n}^2\right>\,,%\nonumber\\
%&=&0\,.
\label{eq:4p_cumulant}
\end{eqnarray}
%\end{widetext}
%
with the condition $m\neq n$ for two positive integers $m$ and $n$ (for details see Sec.~IV~C in Ref.~\cite{Bilandzic:2013kga}).
In this article SC($m$,$n$) normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$~\cite{ALICE:2016kpq,Giacalone:2016afq} is denoted by NSC($m$,$n$):
%
\begin{equation}
\mathrm{NSC}(m,n) \equiv \frac{\mathrm{SC}(m,n)}{\left<v_{m}^2\right>\left<v_{n}^2\right>}\,.
\label{eq:nsc}
\end{equation}
%
Normalized symmetric cumulants reflect only the strength of the correlation between $v_{m}$ and $v_{n}$, while SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics. In Eq.~(\ref{eq:nsc}) the products in the denominator are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$ which suppresses biases from few-particle nonflow correlations. For the two two-particle correlations which appear in the definition of SC$(m,n)$ in Eq.~(\ref{eq:4p_cumulant}), the pseudorapidity gap is not needed, since nonflow is suppressed by construction in this observable. This was verified by HIJING model simulations in Ref.~\cite{ALICE:2016kpq}.

The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anticorrelated, while fluctuations of $v_2$ and $v_4$ are correlated for all centralities~\cite{ALICE:2016kpq}. It was found that the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (midcentral) regimes~\cite{ALICE:2016kpq}. The observed centrality dependence of SC(4,2) cannot be captured by models with constant $\eta/s$, indicating that the temperature dependence of $\eta/s$ plays an important role. These results were also used to discriminate between different parametrizations of initial conditions. It was demonstrated that in the fluctuation-dominated regime (central collisions), Monte Carlo (MC)-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}. 
The first theoretical studies of SC observables can be found in Refs.~\cite{Zhou:2015eya,Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.

\section{Data Analysis}
\label{sec:experiment}
The data sample of $\PbPb$ collisions at the center-of-mass energy $\snn=2.76$~TeV analyzed in this article was recorded by ALICE during the 2010 heavy-ion run of the LHC.
Detailed descriptions of the ALICE detector can be found
in Refs.~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The time
projection chamber (TPC) was used to reconstruct charged particle
tracks and measure their momenta with full azimuthal coverage in the
pseudorapidity range $|\eta|<0.8$. Two scintillator
arrays (V0A and V0C) which cover the pseudorapidity  ranges $-3.7<\eta<-1.7$
and $2.8<\eta<5.1$ were used for triggering and the determination of
centrality~\cite{Aamodt:2010cz}. The trigger
conditions and the event selection criteria are identical to those
described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
Approximately $10^7$ minimum-bias $\PbPb$ events with
a reconstructed primary vertex within $\pm 10$ cm from the nominal
interaction point along the beam direction are selected. Only charged particles reconstructed in the TPC in $|\eta|<0.8$
and $0.2<p_{\rm T}<5$~GeV/$c$ were included in the analysis. The charged track quality cuts
described in Ref.~\cite{Aamodt:2010pa} were applied to minimize
contamination from secondary charged particles and fake tracks.
The track reconstruction efficiency and contamination
were estimated from HIJING Monte Carlo
simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
the collision centrality. The reconstruction efficiency increases with transverse momenta from
70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
constant at $(80 \pm 5)$\% for $p_{\rm T}>1$~GeV/$c$. The estimated
contamination by secondary charged particles from weak decays and
photon conversions is less than 6\% at $p_{\rm T}=0.2$~GeV/$c$ and falls
below 1\% for $p_{\rm T}>1$~GeV/$c$.
The $p_{\rm T}$ cutoff of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effects of jets on the measured correlations. 
Reconstructed TPC tracks constrained to vertex are required to have at least 70 space points (out of a maximum of 159). 
Only tracks with a transverse distance of closest approach to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted. This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc. Tracks with kinks (i.e. tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.

@@

The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution for the whole centrality range analyzed. The systematic uncertainty from the centrality determination was evaluated by using the TPC and silicon pixel detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors. 
The systematic uncertainty on the symmetric cumulants which arises from the centrality uncertainty is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$ vertex) is required to be located within 10 cm of the nominal interaction to ensure uniform detector acceptance for tracks within $|\eta|<0.8$. The systematic uncertainty from the $z$-vertex cut was estimated by reducing the $z$-vertex range to 8~cm and was found to be less than 3\%.
